### 2018-06-22 draft.Rmd
maps added to draft

```{r map, fig.width=6, fig.height=4.5, cashe = TRUE, fig.cap= "Figure 1. Map of Andi villages and their neighbours"}
coord <- read_tsv("data/coordinates.tsv")

@@

map.feature(coord$Language,
            features = coord$Language,
            latitude = coord$Lat,
            longitude = coord$Lon,
            label = coord$label,
            label.hide = FALSE,
            label.fsize = 12,
            label.font = "Times New Roman",
            shape = TRUE,
            zoom.level = 11,
            tile = "Stamen.TonerBackground")
```

>>>>

```{r}

coord <- read_tsv("data/coordinates.tsv")

@@

```

```{r map, fig.width=6, fig.height=4.5, cashe = TRUE, fig.cap= "Figure 1. Andi on the map"}

map.feature(languages = "Andi",
            color = "darkseagreen",
            width = 5,
            zoom.level = 8,
            label = "Andi",
            label.hide = F,
            label.fsize = 12,
            label.font = 'Brill',
            minimap = T)

```

```{r map, fig.width=6, fig.height=4.5, cashe = TRUE, fig.cap= "Figure 1. The Andi villages and their neighbours"}

coord$Language <- factor(coord$Language, levels = c("Chechen", "Avar", "Andi", "Botlikh", "Godoberi", "Karata"))

map.feature(coord$Language,
            features = coord$Language,
            latitude = coord$Lat,
            longitude = coord$Lon,
            width = 8,
            color = c("white", "deepskyblue", "darkseagreen", "aquamarine4", "aquamarine2", "lightblue1"),
            label = coord$label,
            label.hide = FALSE,
            label.fsize = 12,
            label.font = 'Brill',
            zoom.level = 11,
            tile = c("Esri.WorldGrayCanvas"))
```
